Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more work on the conclusions

We presented an unified framework that combines the ParSpec framework
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
%
We showed with concrete examples, how theory-specific QNM calculations of
slowly-rotating BHs in modified gravity theories can be mapped onto the
non-GR parameters of the ParSpec formalism.
%
Put together this allowed us to use the \pSEOB~waveform model to test four
modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
observational data from the LVK events GW150914 and GW200129.

@@

\agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities
and refer to Fig.~\ref{fig:corner_plot_all}}

>>>>

We presented an unified framework that combines the ParSpec framework
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
%
We showed with concrete examples, how theory-specific QNM calculations of
slowly-rotating BHs in modified gravity theories can be mapped onto the
non-GR parameters of the ParSpec formalism.
%
The resulting \pSEOB~waveform model not bias (relative to GR) the inference of
the intrinsic binary parameters as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
Appendix~\ref{app:big_contour},~Fig.~\ref{fig:corner_plot_all}).
%
Put together this allowed us to test four modified gravity theories (EdGB, dCS,
cubic, and quartic EFTs of GR) using observational data from the LVK events
GW150914 and GW200129.

@@

% HS: done
% \agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities
% and refer to Fig.~\ref{fig:corner_plot_all}}
